---
title: "Homework 5"
author: "Tara Ahi"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_color_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))

```


## Problem 1

```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/no arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
  
```

We can see city ID, homicide number, victim demographics (age, race, etc.), city and state where the homicide took place, as well as latitude and longitude. 
Age is being recorded as a character rather than numeric variable because they're sometimes unknown. 
NA variables in CSV will be blanks or unknown.


Focusing on Baltimore...

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

```

Issue with n here, troubleshooting:

```{r eval=FALSE}
baltimore_test = 
  prop.test(
  x = baltimore_summary %>% pull(unsolved),
  n = baltimore_summary %>% pull(n))

baltimore_test %>% 
  broom::tidy()
```


Iterate across cities:

First, write function and test it on some sample cities:

```{r}
prop_test_function = function(city_df) {
  
  city_summary = 
    city_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )
  
  city_test = 
    prop_test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n))
  
  return(city_test)
}

```

```{r eval=FALSE}
prop_test_function(baltimore_df)
```

```{r eval=FALSE}
homicide_df %>% 
  filter(city_state == "AlbuquerqueNM") %>% 
  prop_test_function()
```

Now let's iterate across all cities.

```{r eval=FALSE}
results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))

nested_df %>% 
  filter(city_state == "BaltimoreMD") %>% 
  pull(tidy_results)


```


Make plot showing estimates and confidence intervals:

```{r eval=FALSE}
results_df %>% 
  mutate(city_state == fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

another way to do it:
```{r eval=FALSE}
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>% 
  mutate(
    test_results = map2(unsolved, n, prop.test),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```



## Problem 2

List files:

```{r}
data = list.files(path = "./data/more_data", 
                  pattern = "*csv",
                  full.names = T) %>% 
  map_df(~read_csv(.)) %>% 
  mutate(names = list.files("./data/more_data")) %>% 
  relocate(names)

```

Next, I want to create a new column that designates whether a participant is in the control group or in the experimental group. We use `mutate` to define a new variable in the data frame that is a _function_ of an existing variable.

```{r eval=FALSE}
category_function = function(x) {
  
  if (starts_with("con")) {
    arm = "Control"  
  }
  
  if (starts_with("exp")) {
    arm = "Experiment"
  }
  
}
  
  
```

Iterate the function across columns:

```{r eval=FALSE}
new_df = 
  data %>% 
  mutate(arm = map(data, category_function))
```

We then do a `pivot_longer` and mutate things to make them tidy.

```{r}

```

Finally, the scatterplot:

```{r eval=FALSE}
ggplot(new_df, aes(x = week, y = participant)) +
  geom_point(aes(color = arm))
```



## Problem 3

```{r}
library(tidyverse)

set.seed(10)

iris_with_missing = 
  iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>% 
  janitor::clean_names()

```

There are a few missing values, write a function:

```{r}
fill_in_function = function(vector) {
  
  if (is.numeric(vector)) {
    vector = ifelse(is.na(vector), mean(vector, na.rm = TRUE),vector)  
  }
  
  if (is.character(vector)) {
    vector = ifelse(is.na(vector), "virginica", vector)
  }
  return(vector)
  
}
```

Map across each column and apply the function, put back together as dataframe: 

```{r}
output = map_dfr(iris_with_missing, fill_in_function, .id = "input")

output
```
         
It's all filled in now.


FIN
         
         
         
         
         
         
