---
title: "Homework 5"
author: "Tara Ahi"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_color_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))

```


# Problem 1

```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/no arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
  
```

We can see city ID, homicide number, victim demographics (age, race, etc.), city and state where the homicide took place, as well as latitude and longitude. 
Age is being recorded as a character rather than numeric variable because they're sometimes unknown. 
NA variables in CSV will be blanks or unknown.


Focusing on Baltimore...

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

```

Issue with n here, troubleshooting:

```{r eval=FALSE}
baltimore_test = 
  prop.test(
  x = baltimore_summary %>% pull(unsolved),
  n = baltimore_summary %>% pull(n))

baltimore_test %>% 
  broom::tidy()
```


Iterate across cities:

First, write function and test it on some sample cities:

```{r}
prop_test_function = function(city_df) {
  
  city_summary = 
    city_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )
  
  city_test = 
    prop_test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n))
  
  return(city_test)
}

```

```{r eval=FALSE}
prop_test_function(baltimore_df)
```

```{r eval=FALSE}
homicide_df %>% 
  filter(city_state == "AlbuquerqueNM") %>% 
  prop_test_function()
```

Now let's iterate across all cities.

```{r eval=FALSE}
results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))

nested_df %>% 
  filter(city_state == "BaltimoreMD") %>% 
  pull(tidy_results)


```


Make plot showing estimates and confidence intervals:

```{r eval=FALSE}
results_df %>% 
  mutate(city_state == fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

another way to do it:
```{r eval=FALSE}
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>% 
  mutate(
    test_results = map2(unsolved, n, prop.test),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```



# Problem 2

Make a spaghetti plot for each subject over time but they're all in different files. 

```{r}
tibble(
  files = list.files("./data/more_data")
)

```

Write function or use something liek that to iterate across this file name and read csv to import the files one by one, will get column of datasets.

unnest the column and then you tidy the result, you want a control and experiment arm, it's in wide instead of long format, then make the plot. 



# Problem 3

```{r}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

There are a few missing values, write a function:

```{r}
fill_in_function = function(vector) {
  
  if (is.numeric) {
    
    ...
  }
  
  if (is.charactger) {
    
    ...
  }
  
  
}
```


map across each column and apply the function, put back together as dataframe 




